Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
histogram

```{r, output=FALSE, echo=FALSE}
library(sf) # for map
library(tidyverse) # using only for joining datasets to build map visual
library(RColorBrewer) # for map color scheme
library(tidygeocoder) # to get zip codes of addresses

@@

covid_la <- covid_14day %>% filter(grepl("Los Angeles", geo_merge))
covid_la$area <- gsub("Los Angeles - ", "", covid_la$geo_merge)
```

@@

@@

# ggplot2 ideas

## Histogram

>>>>

```{r DATA, output=FALSE, echo=FALSE}
library(sf) # for map
library(tidyverse) # using only for joining datasets to build map visual
library(RColorBrewer) # for map color scheme
library(tidygeocoder) # to get zip codes of addresses

@@

covid_la <- covid_14day %>% filter(grepl("Los Angeles", geo_merge))
covid_la$area <- gsub("Los Angeles - ", "", covid_la$geo_merge)

evictions_la <- read.csv("Raw_Data/LA_evictions.csv")
```

@@

# Exploratory Data Analysis With ggplot2

## Histogram
```{r}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)

crime_la_monthly <- crime_la %>% group_by(Year)
# convert to date
evictions_la$month_year <- format(as.Date(evictions_la$Date.Received, format="%m-%d-%Y"), "%Y-%m")

# get unique months
unique_months <- data.frame(month_year = sort(unique(evictions_la$month_year)), index = 1:length(unique(evictions_la$month_year)))

evictions_la_indexed <- evictions_la %>% left_join(unique_months, by = "month_year")

ggplot(data = evictions_la_indexed, aes(x = index)) + 
  geom_histogram(bins = nrow(unique_months)) +
  scale_x_continuous(breaks=unique_months$index,
        labels=unique_months$month_year) + 
  theme(axis.text.x = element_text(angle = 285, vjust = 0.5, hjust=1),
        axis.title.x = element_text(vjust = -.75),
        plot.title = element_text(size=12)) + 
  labs(x = "Month and Year of Eviction Notice Receipt", y = "Number of Evictions", title = "Monthly Frequency of Evictions in the City of Los Angeles \nFebruary 2023 to February 2025") +

```{r, echo=FALSE}
# creating dataset for correlations

## Plot 5

## Plot 6

@@
